---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
## Overview
**covid19dbcand** is a smaller version from [dbdataset package](https://github.com/Dainanahan/dbdataset) that contains 75 different data frames that constitute the dataset parsed from [DrugBank](https://www.drugbank.ca). 

The dataset was extracted from the DrugBank XML database via [dbparser](https://docs.ropensci.org/dbparser) R package.

This dataset dedicated to covid-19 potential drugs in [Drugbank](https://www.drugbank.ca/covid-19#drugs). 

It can be used for conveniently exploring and analyzing the contents of the DrugBank database. The dataset is also intended to assist in drug discovery endeavors that plan to make use of the **DrugBank** database.

Moreover; it also can be used to in Machine Learning in many sub-fields such as:

- Natural Language Processing (NLP)
- Web Scrapping
- Visualization

### Installation
As the package size exceeds the limit set by CRAN, it will be hosted on Github only for now. Hence, it could be installed via the following command.

```{r eval=FALSE}
install.packages(covid19dbcand)
```

The datasets will then be available after running the following command:

```{r eval=FALSE}
library(covid19dbcand)
```

## Used Versions
* dbparser: 1.1.2
* Drugbank: 5.1.6



